Visualising Life Satisfaction in Countries across Europe: Individual- and Multi-Level Evidence on Cultural and Pecuniary Factors

### 2019-01-31 LaTex/Paper_fulltext.tex
Altered conclusion

\section{Conclusion}
To conclude this project description it remains to say that this project was set out, trying to keep its stand regarding several different, sometimes conflicting expectations. The ambition to produce high quality analytical insights combining with deep-diving theoretical contextualisation that together contribute to the state of research in the discipline alone is a challenging one. It is met with an ambition of similar challenge in trying to produce a project that allows easy access exploration of the data in question for a lay public that has only little understanding of the statistics or programming involved, while at the same time offering enough substance to be of educational value for the user and inspire further interest for the topic and method of analysis. These are expectational challenges that are similar to the aforementioned trade-off between 'Open Science' and 'Citizen Science'. However, the result of this project is also promising in that it does fulfil many of the expectations that it was met with. The application produced is relatively easy accessible and offers a range of methods of analysis for a substantive amount of variables for individuals, regions and nations. It is possible to produce analytical results on many levels of scientific expertise and sourcing and processing of data is thoroughly documented. There is also a significant amount of theoretical consideration that flew in selection of variables and methods of analysis and that will hopefully inspire interest on th topic of life satisfaction. Among future challenges, there is the quality and access to data, especially for the analysis of countries and regions, which today is incomplete in many cases. There are some remaining challenges specifically for this project, if it is to achieve the its ultimate goal of offering access to a broad public audience, but we hope that with this preliminary project state there first important step are made with many more to come.

	%% The Appendices part is started with the command \appendix; appendix sections are then done as normal sections
\newpage
 \appendix

>>>>

\section{Conclusion}
To conclude this project description, it remains to say that the project outline was, at times, torn between several 
different, sometimes conflicting expectations. The ambition to produce high-quality analytical insights combined with 
deep-diving theoretical contextualisation is a challenging endeavour. Conducting a project that allows easily accessible 
data exploration for lay people is tough in its own right. One the one hand, one has to cater to an audience that has only
little understanding of the statistics or programming behing the figures. On the other hand, 
offering enough substance and educational value to spark further interest on the topic and the method should be assured.
These are expectational challenges that are similar to the aforementioned trade-off between 'Open Science' and 'Citizen
Science'. However, the result of this project is promising in so far as it fulfils many of the expectations that it was set out
to meet. The application produced is easily accessible and offers a range of possibilities for the analysis of various
variables on an individuals, regional, and national level. 
Moreover, data sourcing and processing is thoroughly documented. Lastly, significant theoretical considerations
justify our selection of variables and methods and will hopefully attract others to explore the topic of life satisfaction.\\
Future challenges include sufficient data access and quality, especially regarding countries and regions that are not covered to date.
Despite - or maybe because - of future challenges we are optimistic that this project is just the first destination of a longer journey. 
	%% The Appendices part is started with the command \appendix; appendix sections are then done as normal sections
\newpage
 \appendix
